\documentclass[11pt,a4paper,unicode]{moderncv}
 

% moderncv themes
\moderncvtheme{classic} % optional argument are 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'roman' (for roman fonts, instead of sans serif fonts)
% character encoding
\usepackage[utf8]{inputenc} % replace by the encoding you are using

% adjust the page margins
\usepackage[scale=0.85]{geometry}
% \setlength{\hintscolumnwidth}{3cm} % if you want to change the width of the column with the dates
% \AtBeginDocument{\setlength{\maketitlenamewidth}{6cm}} % only for the classic theme, if you want to change the width of your name placeholder (to leave more space for your address details
% \AtBeginDocument{\recomputelengths} % required when changes are made to page layout lengths
\usepackage{amssymb}
% Hyperlinks
\usepackage[unicode]{hyperref} % to use hyperlinks
\definecolor{linkcolour}{rgb}{0,0.2,0.6} % hyperlinks setup
\definecolor{red}{rgb}{1, 0, 0} % red color
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour, linkcolor=linkcolour}

\def\labelitemi{$\centerdot$}

\firstname{Stephanie} \familyname{Oh}

\address{San Francisco, CA} \phone{224.603.2085} \email{steph@nieoh.com}
\homepage{www.linkedin.com/in/ohstephanie}
 

% to show numerical labels in the bibliography; only useful if you make citations in your resume
\makeatletter \renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}} \makeatother

\nopagenumbers{}

\begin{document}

\vspace*{-6mm}
\maketitle
\vspace*{-6mm}

%===========================================================================
%           Employment
%===========================================================================
\section{Employment}

\cventry{2018 - 19}{Senior Data Scientist}{Lending Club}{San Francisco, CA}{}{}{}
\vspace{-.1cm}
\cvline{}
{\begin{itemize} 
	  \item Built ensemble models to identify potential repeat borrowers representing over \$1.5 billion in personal loans per year. 
	  \item Collaborated with the data engineering team to create data sources in Hive that are robust to data leakage and used for production model development.
	  \item Worked with credit bureau and financial behaviorial features on topics such as NLP in marketing and LTV modeling.
\end{itemize}}
\vspace{-.5cm}


\cventry{2017 - 18}{Senior Data Scientist}{Sentient Technologies}{San Francisco, CA}{}{}{}
\vspace{-.1cm}
\cvline{}
{\begin{itemize} 
	  % \item Experience with visual similarity models and fast POC development to assist business decisions.
	  \item Built and trained a reinforcement learning model for long/short trading.
	  \item Trained and tuned visual similarity models for apparel recommendations. Used a deep Siamese network with apparel images as input and output. 
	  \item Created a basic framework for plugging in different optimization engines to search the space of audience targeting, bidding, and ad creative for digital marketing advertisement.  
	  \item Led development of MVP for full funnel optimization. Productionized feature modeling research code. Helped develop the backend- serving using Flask, the UI with Bootstrap, and productionization with CI/CD leveraging Travis and AWS. 
	  \item Collaborated on and evangelized an open source model management framework - Studio.ML- for data scientists and researchers.  
\end{itemize}}
\vspace{-.5cm}


\cventry{2016 - 17}{Data Science Fellow}{Fellowship.AI}{Oakland, CA}{}{}{}
\vspace{-.1cm}
\cvline{}
{\begin{itemize} 
	  \item Developed a long/short trading model for a hedge fund client. Used reinforcement learning with a DQN network with experience replay and epsilon-decay in TensorFlow. 
	  \item Led biweekly status update meetings with the project manager and scientist at the hedge fund.
\end{itemize}}
\vspace{-.5cm}


\cventry{2015 - 16}{Manager of Education Software Technology}{Wolfram Research}{San Francisco, CA}{}{}{}
\vspace{-.1cm}
\cvline{}
{\begin{itemize} 
	  \item Hired, trained, and managed a remote group of developers working on education-focused technologies such as Wolfram|Alpha. 
	 % \item Create and execute product roadmaps for Wolfram's educational tools, such as expanding the college-level math content for Wolfram|Alpha.
	 % \item Manage, edit and create education content such as programming challenges, Wolfram|Alpha math content, and exercises for a introductory programming book. 
	 % \item Integrated Wolfram|Alpha with other classroom technologies like Google Drive.
	 %  \item Solve backend development problems such as user data management, cloud deployment and automated code-grading. 
	  \item Led development and content meetings with CEO, Stephen Wolfram.
	 %  \item Interview, hire and train new developers in the company's tools and development language. 
 \end{itemize}}
\vspace{-.5cm}


\cventry{2013 - 15}{Developer}{Wolfram Research}{Boston, MA}{}{}{}
\vspace{-.1cm}
\cvline{}
{\begin{itemize} 
	\item Developed continuously deployed revenue generating math content for \url{wolframalpha.com}.
	% \item Exhibited and presented at national education and software development-based conferences.
	% \item Developed random math problem generation for Wolfram Problem Generator.
	% \item Taught coding, Topology, and Graph Theory at a summer camp for high school students.
\end{itemize}}
\vspace{-.5cm}

%===========================================================================
%           Computer Skills
%===========================================================================

\section{Skills}

\cvline{Languages}{Mathematica, Python, SQL, Korean}
\cvline{Frameworks}{NumPy, pandas, scikit-learn, Keras, TensorFlow, Presto, XGBoost}
\cvline{Learning}{Machine Learning, Deep learning, Reinforcement learning, Deep Q-learning}
\cvline{Miscellaneous}{Git, AWS, Travis, Docker, HTML, \LaTeX, Camtasia}
\cvline{Interests}{Powerlifting, scuba diving, snowboarding}


%===========================================================================
%           Education
%===========================================================================
\section{Education}

\cventry{2013}{MS in Mathematics}{Purdue University}{}{}{}%{\textit{3.6/4.0}}

\cventry{2011}{BA in Mathematics with Honors}{Northwestern University}{}{}{}
%\vspace{-1mm}
%\cvline{}{\small Honor thesis on Expander Graphs (2011)}
%\vspace{-1mm}
%\cvline{}{\small Recipient of merit scholarships for outstanding academic achievement.} %{\textit{3.64/4.0}}
\cventry{2009-2010}{Budapest Semesters in Mathematics}{}{Budapest, Hungary}{}{}  
\cventry{2007}{High School Diploma}{The Hill School}{Pottstown, PA}{}{}
\vspace{-1mm}

%Budapesti M\H{u}szaki \'{e}s Gazdas\'{a}gtudom\'{a}nyi Egyetem

%===========================================================================
%           Professional Affiliations and Development
%===========================================================================
%\section{Professional Affiliations and Development}

%\cvline{2015}{Exhibitor and speaker at DeveloperWeek as part of GirlDevWeek}{}{}{}{}

%\cvline{2014}{Exhibited at EDUCAUSE's annual conference.}{}{}{}{}

%\cvline{2014}{Exhibited, presented, and ran focus groups at American Mathematical Association of Two Year Colleges' annual conference.}{}{}{}{}

%\cvline{2011-13}{Member of American Mathematical Society.}{}{}{}{}

%\cvline{2011}{Presented at the Joint Mathematics Meeting on Expander Graphs}{}{}{}{}

%\cvline{2010-11}{Member of Mortar Board national honor society.}{}{}{}{}

%\cvline{2010}{NSF funded research on Expander Graphs with professor Darren Long at UCSB.}

%\cvline{2008}{Selected for and attended Carleton College's Summer Math Program for Women.}{}{}{}{}


%\section{Qualities}
%\cvline{Personal skills:}{Strong analytical, problem-solving and communication skills; eager to
%  learn and develop new skills; ability to design creative solutions.}  \cvline{Experience
%  with:}{Working in a small team to conceive and develop a new product; explaining technical details in understandable terms; %training students to achieve mathematical maturity (or should I say technical proficiency?). }

%\section{Extracurricular}
%\cvline{Languages}{English and Korean.}{}
%\cvline{Interests}{Powerlifting, scuba diving and snowboarding.}


%===========================================================================
%           Languages
%===========================================================================

%\section{Languages}

%\cvline{Native}{English, Korean}{} 

%\cvline{Basic}{French, German}{}


%===========================================================================
%          Extracurricular
%===========================================================================

%\section{Extracurricular}
%\cvline{Interests:}{Powerlifting, snowboarding, playing the piano, and cooking.}

%\cvline{Community service:}{Participated in a clinical trip providing free medical attention in southern
%  Vietnam.  \newline Tutored Korean K-12 students in math and English.}

%=====================================================
% Cover Letter
%=====================================================
\iffalse
\clearpage

\recipient{\textcolor{red}{HR Departmnet}}{Corporation\\123 Pleasant Lane\\12345 City, State} % Letter recipient
\date{\today} % Letter date
\opening{\textcolor{red}{Dear McKinsey Person},} % Opening greeting
\closing{Most Sincerely,} % Closing phrase
\enclosure[Attached]{curriculum vit\ae{}} % List of enclosed documents

\makelettertitle % Print letter title
	I would like to apply for an \textcolor{red}{Associate position at McKinsey's Los Angeles office}. Enclosed is a copy of my CV highlighting my education and experience, including my current job as a software developer for Wolfram Research-- a computation software company and maker of Mathematica. 
		
\vspace{3mm}  
Through past experience, I have gained the presentation and analytical skills ideal for succeeding at McKinsey. Working as a Calculus teaching assistant taught me how to present technical solutions effectively. Additionally, I can apply my knowledge from the tech industry to help global clients achieve the virtualization necessary to thrive in the age of this impending global resource revolution. As reported in the \emph{McKinsey Quaterly}, a fast rate of virtualization is a key indicator of a company's competitiveness. 

%I received a bachelor's with honors from Northwestern University and a master's from Purdue University in Mathematics. Currently, I am working as a software developer for Wolfram Alpha LLC. 
%I am ready to redirect my analytical skills to producing tangible results for clients as well as my leadership skills to managing ambitious and innovative projects.
\vspace{3mm}
At Wolfram Alpha, I often work on exploratory projects prior to team assignment. I have been successful in this position due to my unique type of leadership. I identify the strengths and personalities of my coworkers and employ their skills to add depth to my projects. For example, I was successful in presenting a comprehensive prototype for a new technical education initiative in a recent meeting with the CEO of Wolfram Alpha. I recruited a few coworkers, with whom my relationship had been strictly social, to be my UX developer and domain specific expert. Together, we were able to realize my vision and create a complete prototype to move the project into the next step of development.

\vspace{3mm}
My math background from Northwestern University and Purdue University has trained me to recognize hidden relationships in seemingly disparate concepts and to devise creative solutions to any problem. While maintaining content for wolframalpha.com, I came across a strange numerical error. I identified and fixed the error and improved the speed of the program by 1000$\%$, using skills acquired during graduate school. As the content I develop goes live weekly, I am also experienced working in a result-oriented environment.

\vspace{3mm}
I have leveraged my unique education background from four different countries to develop a creative point of view and adaptability. Unlike other applicants who may have problems adjusting to the rigorous environment at McKinsey, I am ready to use my analytical intuition to thrive at the company. 

\vspace{3mm}
Thank you for your consideration. I look forward to discussing opportunities with you.

\vspace{3mm}
\makeletterclosing % Print letter signature
\fi
\end{document}
