\documentclass[11pt,a4paper,unicode]{moderncv}
 

% moderncv themes
\moderncvtheme{classic} % optional argument are 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'roman' (for roman fonts, instead of sans serif fonts)
% character encoding
\usepackage[utf8]{inputenc} % replace by the encoding you are using

% adjust the page margins
\usepackage[scale=0.85]{geometry}
% \setlength{\hintscolumnwidth}{3cm} % if you want to change the width of the column with the dates
% \AtBeginDocument{\setlength{\maketitlenamewidth}{6cm}} % only for the classic theme, if you want to change the width of your name placeholder (to leave more space for your address details
% \AtBeginDocument{\recomputelengths} % required when changes are made to page layout lengths
\usepackage{amssymb}
% Hyperlinks
\usepackage[unicode]{hyperref} % to use hyperlinks
\definecolor{linkcolour}{rgb}{0,0.2,0.6} % hyperlinks setup
\definecolor{red}{rgb}{1, 0, 0} % red color
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour, linkcolor=linkcolour}

\def\labelitemi{$\centerdot$}

\firstname{Stephanie} \familyname{Oh}

\address{San Francisco, CA} \phone{224.603.2085} \email{steph@nieoh.com}
\homepage{www.linkedin.com/in/ohstephanie}
 

% to show numerical labels in the bibliography; only useful if you make citations in your resume

\makeatletter \renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}} \makeatother
\nopagenumbers{}

\begin{document}

\vspace*{-6mm}

\vspace*{-6mm}


\recipient{{HR Department}}{Pinterest} % Letter recipient

\date{\today} % Letter date


\opening{{Dear Pinterest},} % Opening greeting
\closing{Most Sincerely,} % Closing phrase
\enclosure[Attached]{curriculum vit\ae{}} % List of enclosed documents

\makelettertitle % Print letter title
	I would like to apply for a Data Scientist position the San Francisco office. I have attached a copy of my CV with my education and experience, including my recent experience as a deep learning engineer for a hedge fund, as well as my current job as a software developer for Wolfram Research. 
			
\vspace{3mm}  
	Both Wolfram|Alpha and Pinterest rely heavily on continuous deployment and low latency systems. The bulk of my responsibilities at Wolfram include creating math content which is automatically tested and deployed on a weekly basis and maintaining and debugging the content currently available on wolframalpha.com. I believe the agile development process would translate to Pinterest. In addition, wolframalpha.com is a mass user-based system, as is Pinterest, so I am constantly keeping the user experience and limitations in mind while developing content. 
	
\vspace{3mm}  
	My experience working on deep learning models for a hedge fund at StartupML has further enforced my statistical modeling background from my Master's degree, as well as, my prototyping skills from working on projects at Wolfram Research. At StartupML, I worked directly with the clients to understand their data and needs. As the lead engineer, I had to research various models and prototypes to balance computational resources and model accuracy. I worked with TensorFlow implementing different LSTM models as well as reinforcement learning models. 
	

\vspace{3mm}	
	The main reason for my interest lays in the data that Pinterest owns. Whilst working for a hedge fund was enlightening, I am much more interested in data that represents humans and their every day lives.
	
\vspace{3mm}  
	Thank you for your consideration. I look forward to discussing opportunities with you. I'm excited to applying for a position where my technical interests and skills align with my personal interests. 

\makeletterclosing % Print letter signature

\end{document}
